Dependent Object Types

### 2012-08-05 article.tex
simplify apps

Now, consider the term
\begin{align*}
&\mlnew u {X \ldefs{ l = u }}{
(\app {(\abs y {\Top \tfun Y} {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})}).l
}
\end{align*}

The term type-checks because the term $t=(\app {(\abs y {\Top \tfun Y}
  {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})})$ has type
$Y$, so we can apply $\textsc{term-$\ni$}$ for $l$. However, the term
$t$ eventually steps to $(\app {(\abs x X x)} u)$ which has type $X$,
so we cannot apply $\textsc{term-$\ni$}$ for $l$ because of the
self-reference ($z.L_a$).

@@

\begin{align*}
&\mlnew b {\Top \mlrefine z {&&\Ldecl X \Top \Top&\\
&&&\ \ldecl l {z.X}&}\ldefs{l = b}}{
\mlnew a {\Top \mlrefine z {\ldecl i {\Top \mlrefine z {&&&\\
&&&\Ldecl X \Bot \Top\\
&&&\ldecl l {z.X}}}&}\ldefs{i = b}}}{
\app {(\abs x \Top x)} {(\app {(\abs x {a.i.X} x)} {a.i.l})}}
\end{align*}

>>>>

Now, consider the term
\begin{align*}
&\mlnew u {X \ldefs{ l = u }}{
\app {(\abs y {\Top \tfun Y} {\app y u})} {(\abs d \Top {\app {(\abs x X x)} u})}.l
}
\end{align*}

The term type-checks because the term $t=\app {(\abs y {\Top \tfun Y}
  {\app y u})} {(\abs d \Top {\app {(\abs x X x)} u)}}$ has type
$Y$, so we can apply $\textsc{term-$\ni$}$ for $l$. However, the term
$t$ eventually steps to $\app {(\abs x X x)} u$ which has type $X$,
so we cannot apply $\textsc{term-$\ni$}$ for $l$ because of the
self-reference ($z.L_a$).

@@

\begin{align*}
&\mlnew b {\Top \mlrefine z {&&\Ldecl X \Top \Top&\\
&&&\ \ldecl l {z.X}&}\ldefs{l = b}}{
\mlnew a {\Top \mlrefine z {\ldecl i {\Top \mlrefine z {&&&\\
&&&\Ldecl X \Bot \Top\\
&&&\ldecl l {z.X}}}&}\ldefs{i = b}}}{
\app {(\abs x \Top x)} {\app {(\abs x {a.i.X} x)} {a.i.l}}}
\end{align*}
